The Right Way to Search Evolving Graphs

### 2016-01-28 paper.tex
change conclusion

This paper introduced the generalization of BFS to evolving graphs and presented
an equivalent formulation using linear algebra. The concept of temporal paths
connecting active nodes turns out to be critical for the correct generalization
of BFS to evolving graphs. An efficient implementation of BFS on evolving
graphs is now available as a open source Julia package.

% This paper leaves important extensions open for further research. First, extensions
% of BFS to weighted evolving graphs can provide more valuable information when the degree of connectivity is available in the data.
% Second, efficient algebraic representations and algorithms need to be addressed.
% One major advantage of representing evolving graphs as sparse matrices
% is the matrix representation is highly structured so it is easy to design
% high performance parallel implementation.
% Third, depth-first search and other graph traversal algorithms can be
% extended using similar ideas.

>>>>

This paper contemplated one of basic archetypes of graph traversal algorithms
for evolving graphs.
Although rarely mentioned in previous papers,
we showed the concept of node activeness is actually crucial for designing correct and efficient algorithms for evolving graphs.

% This paper introduced the generalization of BFS to evolving graphs and presented
% an equivalent formulation using linear algebra. The concept of temporal paths
% connecting active nodes turns out to be critical for the correct generalization
% of BFS to evolving graphs. An efficient implementation of BFS on evolving
% graphs is now available as a open source Julia package.
% This paper leaves important extensions open for further research. First, extensions
% of BFS to weighted evolving graphs can provide more valuable information when the degree of connectivity is available in the data.
% Second, efficient algebraic representations and algorithms need to be addressed.
% One major advantage of representing evolving graphs as sparse matrices
% is the matrix representation is highly structured so it is easy to design
% high performance parallel implementation.
% Third, depth-first search and other graph traversal algorithms can be
% extended using similar ideas.
